Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-14 paper/paper.tex
undoing a mistake

In this section we show a lower bound of $\Omega(k \cdot \ell)$.
The constructed input sequence allows OPT to move to a perfect partition, and hence
the construction also constitutes a lower bound for \OBRP{}.
This complements an upper bound of $O(k \cdot \ell)$
for \PPOBRP{} that we present in Section \ref{sec:ppl}.

>>>>

In this section we show a lower bound of $\Omega(k \cdot \ell)$ for \OBRP{}.
The constructed input sequence allows OPT to move to a perfect partition, and hence
the construction also constitutes a lower bound for \PPOBRP{}.
This complements an upper bound of $O(k \cdot \ell)$
for \PPOBRP{} that we present in Section \ref{sec:ppl}.
